### 2015-02-14 fundamentals/impl.tex
spell checked

The DRE consists of three steps: supply-demand information gathering, resource
exchange solution, and trade execution. Importantly, each step is agnostic with
respect to the exchange of resources in question, i.e., the same procedure is
used for both Materials and Products. The information-gathering step consists of
three phases. First, consumers of commodities denote both the quantity of a
commodity they need to consume as well as the target isotopics, or quality, by
posting their demand to the market exchange as a series of \textit{requests}. An
optional collection of demand constraints are associated with each collection of
requests. Collections of requests may be grouped together, denoting
\textit{mutual} requests that represent demand for some common purpose. For
example, a reactor may request UOX and MOX fuel mutually, indicating that either
will satisfy its demand for fuel. Suppliers then respond to the series of
requests with a \textit{bid}. A bid supplies a notion of the quantity and
quality of a resource to match a request. Suppliers may add an arbitrary number
of constraints to accomany bids. For example, an enriched UOX supplier may
supply both a natural Uranium and SWU constraint. Any potential resource
transfer may be denoted as \textit{exclusive}. An exclusive transfer must either
be met fully or not at all in order to support concepts such as the the trading
of individual reactor assemblies. Finally, requesting facilities, institutions
and regions may apply \textit{preferences} to each potential request-bid pairing
based on the proposed resource transfer. Therefore, an institution can apply a
higher preference to a partner to which it is congenial; similarly, a region may
negate any transfers of material which have a higher Uranium enrichment than is
allowable.

The DRE may be solved either optimally by a mathematical program or
approximately by a simulation-based heuristic \TODO{cite}. If any trade is
denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
then either a heuristic must be used or exchanges must be respresented as
Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear
Programming (LP) model may be used. In practice, LPs solve much faster than
MILPs. However, the capability to model both exists in \Cyclus in order to
provide users with the desired level of fidelity.

>>>>

The DRE consists of three steps: supply-demand information gathering, resource
exchange solution, and trade execution. Importantly, each step is agnostic with
respect to the exchange of resources in question, i.e., the same procedure is
used for both Materials and Products. The information-gathering step consists of
three phases. First, consumers of commodities denote both the quantity of a
commodity they need to consume as well as the target isotopics, or quality, by
posting their demand to the market exchange as a series of \textit{requests}. An
optional collection of demand constraints are associated with each collection of
requests. Collections of requests may be grouped together, denoting
\textit{mutual} requests that represent demand for some common purpose. For
example, a reactor may request UOX and MOX fuel mutually, indicating that either
will satisfy its demand for fuel. Suppliers then respond to the series of
requests with a \textit{bid}. A bid supplies a notion of the quantity and
quality of a resource to match a request. Suppliers may add an arbitrary number
of constraints to accompany bids. For example, an enriched UOX supplier may
supply both a natural Uranium and SWU constraint. Any potential resource
transfer may be denoted as \textit{exclusive}. An exclusive transfer must either
be met fully or not at all in order to support concepts such as the the trading
of individual reactor assemblies. Finally, requesting facilities, institutions
and regions may apply \textit{preferences} to each potential request-bid pairing
based on the proposed resource transfer. Therefore, an institution can apply a
higher preference to a partner to which it is congenial; similarly, a region may
negate any transfers of material which have a higher Uranium enrichment than is
allowable.

The DRE may be solved either optimally by a mathematical program or
approximately by a simulation-based heuristic \TODO{cite}. If any trade is
denoted as exclusive, e.g., if an analyst desires an assembly-fidelity model,
then either a heuristic must be used or exchanges must be represented as
Mixed-Integer Nonlinear Programs (MILP). If no exclusive trades exist, a Linear
Programming (LP) model may be used. In practice, LPs solve much faster than
MILPs. However, the capability to model both exists in \Cyclus in order to
provide users with the desired level of fidelity.
